---
title: "Milestone 4"
author: "Ruth Zheng"
date: "2/28/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}

library(stargazer)
library(lmtest)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(gt)
```

# INTRODUCTION

Experimental footnote \footnote{This is an experimental footnote}. 

# DATA TABLE

```{r, echo = FALSE}

black <- rpois(1,20)
white <- rpois(1,50)
asian <- rpois(1,20)
other <- rpois(1,10)

data = data.frame(cbind(c("black","white","asian","other"), c(black, white, asian, other)))

fake.data <- 
  as_tibble(data) %>%
  rename(Race = X1) %>%
  rename(Arrivals = X2)

gt_tbl <- gt(data = fake.data) 
gt_tbl

```

# REGRESSION TABLE

```{r, echo = FALSE}

fit1 <- lm(rnorm(50,20,1) ~ rnorm(50,0,10), data = data)
fit2 <- lm(rnorm(50,20,1) ~ rnorm(50,0,5), data = data)
fit3 <- lm(rnorm(50,20,1) ~ rnorm(50,0,1), data = data)

# I'm getting this error that the length of NULL cannot be changed. When I looked up what this means, it seems to be an issue with the 
# version of the gt package that i installed. 

stargazer(fit1,  fit2, fit3, title="Experimental Regressions of Independent Normals",
          dep.var.labels=c("Support Supply Increase"),dep.var.labels.include = F, dep.var.caption = "",
          column.labels=c("Model1","Model2","Model3"),
          covariate.labels=c("High Variance","Moderate Variance","Low Variance"),
          align=T, type="text",
          ifont.size = "small", omit.table.layout = "n")

```


# REFERENCES

Altshuler, Alan A., and David E. Luberoff. 2003. \textit{Mega-Projects: The Changing Politics of Urban Public Investment.} Washington, DC: Brookings Institution Press.

Angotti, Tom. 2008. \textit{New York For Sale: Community Planning Con- fronts Global Real Estate.} Cambridge, MA: MIT Press.
Autor, David H., Christopher J. Palmer, and Parag A. Pathak. 2014. “Housing Market Spillovers: Evidence from the End of Rent Con- trol in Cambridge, Massachusetts.” Journal of Political Economy 122 (3): 661–717.

Banfield, Edward C., and James Q. Wilson. 1963. \textit{City Politics.} Cambridge, MA: Harvard University Press.