---
title: "Milestone 7"
author: "Ruth Zheng"
date: "4/17/2020"
output:
  html_document: default
  pdf_document: default
---

  - \usepackage{array}       
  - \usepackage{tabularx}
  - \usepackage{dcolumn} 

# Abstract

Hankinson (2018) shows that renters exhibit "Not in My Back Yard" (NIMBY) behavior on par with homeowners in high-rent cities despite overall support for a housing supply increase. This increased likelihood to reject policy proposals that create new housing helps explain the affordable housing crisis in major American cities. 

# Introduction

Using original data sets from an exit poll in San Francisco and a nation-wide survey, Hankinson shows that renters are more likely to exhibit NIMBY-ism when they live in high density cities with high price levels controlling for other demographic characteristics -- hankinson demonstrates this statistically significant and positive relationship between neighborhood price levels and two response variables: one indicating opposition to a housing supply increase and the other support for a ban on neighborhood development in both "ordinary" data sets and a set from a nation-wide conjoint survey. The data also confirms the prevailing assumption that renters are more likely to support housing supply increases in general. Hankinson reasons a causal mechanism for this surprising trend may be that renters in high-rent neighborhoods fear that new housing may spur gentrification which would only further drive rent up. Exploring this hypothesis, he shows a significant and positive relationship between housing price-related anxiety and renters' likelihood for exhibiting NIMBY-ism.  

# Literature Review

In the past 30 years, the housing market has seen a trend of widening inequality (Glaeser, Gyourko, and Saks 2005). Prices in the top quintile have dramatically increased, particularly in crowded, “superstar” cities such as San Francisco, New York City, and Los Angeles. Yet, the resulting housing shortage cannot be attributed to a natural supply ceiling alone (Glaeser, Gyourko, and Saks 2008; Solnit and Schwartzenberg 2000). Glaeser and Gyourko find that in Manhattan prices are twice their supply costs (Glaeser, Gyourko, and Saks 2008). Likewise, Barton demonstrates that in San Francisco, high rents cannot be accounted for by higher real value -- that is, quality, operating costs, and construction costs (Barton 2011). They argue that the decoupling of supply and demand in Manhattan and other major cities must be attributed at least in part to regulation constraining the housing supply (Glaeser, Gyourko, and Saks 2008). Specifically, land-use regulations are associated with reductions in construction activity and higher prices (Glaeser and Ward 2008; Ilhanfeldt 2007). In fact, the responsiveness of the housing supply to increased demand seems to depend significantly on land use and planning regulations (Caldera and Johansson 2013). This is particularly true in high-price locales such as the greater Boston area (Glaeser and Ward 2008) and the San Francisco Bay Area (Kok, Monkkonen, and Quigley 2014).

It is generally accepted that homeowners have an incentive to support regulations that raise the value of their homes (Glaeser, Gyourko, and Saks 2005; Quigley and Rosenthal 2005; Rohe and Stewart 1996). Typically higher income homeowners are the ones who dominate local politics underlying land use enactments (Quigley and Rosenthal 2005). On the other hand, renters, who usually want lower prices, are expected to support policies and public spending that favor constructing new housing (Brunner, Ross, and Simonsen 2015; Desmond 2017). However, this dynamic cannot entirely explain persistent supply-discouraging regulations in major cities where homeownership rates are lower and pale in comparison to renters. 

Hankinson hypothesizes that in high-rent cities, renters adopt a form of "Not in My Back Yard-ism" (NIMBY-ism). This would give rise to a collective action problem in the political-economy of local housing wherein despite supporting city-wide housing supply increases and other policies favoring affordable housing, renters oppose such policies in their own neighborhoods. As a result, no neighborhood is politically willing to bear the cost of new housing. While there is a rich existing literature on NIMBY-ism among homeowners (Dear 1992; Schively 2007), there has been comparatively little research done on the appearance of this behavior among renters (Fischel 2000). In fact, renters are expected to exhibit lower levels of NIMBY-ism as the ephemerality of renting means they have less of a stake in the good or bad things that happen in their neighborhoods (Moomau and Morton 1992). Renters' behavior in high-rent cities demands closer examination. What is driving renters to continue to enact housing regulations? And, what external and/or demographic factors cause renters policy behavior to become sensitive to the proximity  of proposed new housing? 


# Replication

Hankinson's original paper includes 27 figures. I have replicated 21 of them. Those that I have not replicated are mainly clarifying tables, that is they include summary statistics, demonstrate theoretical results, or attempt to illustrate a hypothetical example. I chose not to replicate these tables because they do not directly pertain to the actual analysis of Hankinson's data set and thus do not contribute to answering the research question about what factors are associated with renters exhibiting NIMBY behavior. 

# Extension

I extend Hankinson's analysis by going beyond an OLS linear model and using logistic regression. Logistic regression allows us to consider the possibility that the relationship between home ownership status and NIMBY-ism is not linear. It enables one to model probabilities continuously while ols can only give discrete outcomes. I refit a bivariate, full, and full with fixed effects model for the national data set with the logit of the probability of supporting the policy proposal of a 10\% increase in housing supply as the response variable. 

```{r load packages, include = FALSE}
library(stargazer)
library(lmtest)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(gt)
library(janitor)
library(sandwich)
library(cjoint)
```


```{r read data, include = FALSE}
socpoc<-read.csv("data/socpocAPSR.csv", stringsAsFactors = F)

#assign ownership groups
renters.socpoc<-subset(socpoc, own==0)
owners.socpoc<-subset(socpoc, own==1)


## Simple Logistic

model_1 <- glm(supply_dummy ~ own, socpoc, family = "binomial")
model_1_se<-sqrt(diag(vcovHC(model_1, type="HC1")))


## Full

model_2 <- glm(supply_dummy ~ own +scale(ideology)+scale(log(income)) + whitenh  +age + male, subset(socpoc), family = "binomial")
model_2_se<-sqrt(diag(vcovHC(model_2, type="HC1")))

# Full w/ fixed effects

model_3<- glm(supply_dummy ~  own +scale(ideology)+ scale(log(income))+ whitenh  + age + male +factor(name), socpoc, family = "binomial")
model_3_se<-sqrt(diag(vcovHC(model_3, type="HC1")))


```

```{r, echo = FALSE, results = 'asis'}
# Create Regression Table

stargazer(model_1,  model_2 , model_3, title="Probability of Supporting 10 Percent Supply Increase", label="supply_7",
          dep.var.labels=c("Support Supply Increase"),dep.var.labels.include = F, dep.var.caption = "",
          column.labels=c("Bivariate","Full","Full with Fixed Effects"),
          covariate.labels=c("Homeownership","Ideology","Income, Log","White, Non-Hispanic","Age","Male"),
          omit.stat = c("ser", "f"), digits=2, align=T, type="latex",
          initial.zero = F,  font.size = "small", star.cutoffs = NA, omit.table.layout = "n",
          se=list(model_1_se, model_2_se, model_3_se), no.space=T,omit=c("name"))

```



# Appendix

# Works Cited