---
title: "Milestone 6"
author: "Ruth Zheng"
date: "4/3/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# INTRODUCTION

## On Replication

I have listed every table and figure from the paper in the order in which they appear. Those that I have successfully replicated are included, while there is a blank for those that I have not replicated. Hankinson's original paper includes 27 figures. I have replicated 21 of them. Those that I have not replicated are mainly explanatory tables, that is they include summary statistics, demonstrate theoretical results, or attempt to illustrate a hypothetical conjoint survey. I chose not to replicate these tables because they do not directly pertain to the actual analysis of Hankinson's data set and thus do not contribute to answering the research question about what factors are associated with renters exhibiting NIMBY behavior. 

## Proposed Extension

In his paper, Hankinson uses the San Francisco specific and Non-Conjoint National Survey data sets to explore differing levels of NIMBY-ism exhibited by renters and homeowners. He measures this outcome using two binary response variables, whether they indicate support for a 10\% supply increase in housing and whether they support a ban on neighborhood development. In both the San Francisco city-specific set which he collects from exit-polling, and the nation-wide survey data, Hankinson considers the demographic controls through the following covariates: homeownership status, Ideology, Income, Race, Age, and Gender. For the San Francisco set he runs two models for each response variable using the lm command: a bivariate regression and a full model including all of the predictors. For the nation-wide data set, Hankinson runs three models: a bivariate regression, a full model, and a full model including municipal fixed effects (holding municipality constant). 

I would like to extend Hankinson's analysis by going beyond an OLS linear model and using logistic regression. I think this would be appropriate for two reasons. First, using a linear approximation runs the risk of breaking axioms of probability when considering a binary response variable because while it is estimating probabilities, it is possible for the predicted value at certain values for the covariates to go outside of 0 and 1. Second, logistic regression allows us to consider the possibility that the relationship between home ownership status and NIMBY-ism is not linear. It enables one to model probabilities continuously while ols can only give discrete outcomes. I will then re-fit these four models for the SF data set and six models for the nation-wide set using logistic and interpret the results. Then I would like to compare the results with those found using the LM command. Finally, I will discuss the discrepencies (or lack thereof). This will be informed by Chapters 13 and 14 of RAOS. 

Another extension I will consider is implementing variable selection. For example, are all the demographic controls Hankinson includes in his final regression outputs necessary? Or might they be causing overfitting to the data? I could use a step function using AIC. 


# REPLICATION RESULTS

```{r load packages, include = FALSE}
library(stargazer)
library(lmtest)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(gt)
library(janitor)
library(sandwich)
library(cjoint)
```

```{r read data, include = FALSE}
socpoc<-read.csv("socpocAPSR.csv", stringsAsFactors = F)

#assign ownership groups
renters<-subset(socpoc, own==0)
owners<-subset(socpoc, own==1)

```

```{r Read Data and Clean National Conjoint, include = FALSE}

conjoint4<-read.csv("conjointDataAPSR.csv")
table(conjoint4$own)
#relevel
conjoint4$distance <- factor(conjoint4$distance,levels= c("2 miles (40 minute walk)", "1 mile (20 minute walk)", "1/2 mile (10 minute walk)","1/8 mile (2 minute walk)"))
conjoint4$community <- factor(conjoint4$community,levels= c("No opinion", "Support the building", "Oppose the building"))
conjoint4$affordable <- factor(conjoint4$affordable,levels= c("None of the units", "One-quarter of the units", "Half of the units", "All of the units"))
conjoint4$height <- factor(conjoint4$height,levels= c("2 stories", "3 stories", "6 stories", "12 stories"))
conjoint4$site <- factor(conjoint4$site, levels=c("Empty building","Parking lot","Open field","Historically-designated building"))
names(conjoint4)
#reclassify items as factor
cols<-c("own", "whitenh", "nearby","conjoint_first","rich", "luxury")

conjoint4[cols] <- data.frame(apply(conjoint4[c(cols)], 2, as.factor))

# dummies
conjoint4$liberal<-as.factor(ifelse(conjoint4$ideology>4,1,ifelse(conjoint4$ideology<4,0, NA)))
conjoint4$city_interest_low<-as.factor(ifelse(conjoint4$city_interest<0,1,0))

#define subgroups/dummies
renters<-subset(conjoint4, own==0)
owners<-subset(conjoint4, own==1)

#define affordability levels
renters_aff<-subset(renters, aff_housing==1)
renters_lux<-subset(renters, aff_housing==0)

owners_aff<-subset(owners, aff_housing==1)
owners_lux<-subset(owners, aff_housing==0)

```

```{r Read Data SF, include = FALSE}

# Read in Data

final<-read.csv("sfDataAPSR.csv", stringsAsFactors = F)

owners<-subset(final, ownership_dummy==1)
renters<-subset(final, ownership_dummy==0)

# Experiment randomization

control<-subset(final, version==5 | version==6)
control_owners<-subset(control, ownership_dummy==1)
control_renters<-subset(control, ownership_dummy==0)

control_owners_yes<-subset(control_owners, ten_plan_dummy==1)
control_owners_no<-subset(control_owners, ten_plan_dummy==0)

control_renters_yes<-subset(control_renters, ten_plan_dummy==1)
control_renters_no<-subset(control_renters, ten_plan_dummy==0)

```

# IN-TEXT RESULTS

### Table 1. Expected Support for New Housing Development by Spatial Scale (Macroscale v. Microscale).

### Figure 1. Support for a Neighborhood Ban on New Development by Support for a 10% Increase in the City’s Housing Supply

```{r Figure 1, echo = FALSE}

support<-c(.37, .50, .52, .81)
Tenant<-c("Homeowners", "Homeowners", "Renters", "Renters")
supply<-c("Pro-Supply", "Anti-Supply","Pro-Supply","Anti-Supply")
supply<-factor(supply, levels=c("Pro-Supply", "Anti-Supply"))

ban_plot<-data.frame(Tenant, support, supply)

exitpoll_ban<-ggplot(data=ban_plot, aes(x=Tenant, y=support, fill=Tenant))+
  geom_bar(colour="black",stat="identity", position=position_dodge()) + facet_wrap(~supply) +
  ylab("Support (Percent)") + theme(legend.position="none") +ggtitle( "Support for Micro-scale Ban by Support for Macro-scale Supply")+
  theme_bw()+scale_fill_grey()

exitpoll_ban
```

### Figure 2. Example of the Conjoint Task

### Table 2. Attributes and Levels

### Figure 3. Effect of Proximity on Homeowners by Affordability of Proposed Housing

```{r Figure 3 code, include = FALSE, cache = TRUE}

# FIGURE 3. Homeowners, Proximity by Affordability ####


# Use AMCE to run regressions

owners_luxury_mod<-amce(select ~ distance  + community + height + site + tenant + units,
                        data= owners_lux , cluster=T,  respondent.id = "CaseID")
owners_affordable_mod<-amce(select ~ distance  + community + height + site + tenant + units,
                            data=owners_aff, cluster=T,  respondent.id = "CaseID")
owners_luxury_mod_frame<-data.frame(Variable=(summary(owners_luxury_mod)$amce)$Level,
                                    Coefficient = (summary(owners_luxury_mod)$amce)$Estimate,
                                    SE=(summary(owners_luxury_mod)$amce)$'Std. Err',
                                    modelName="Market Rate")
owners_affordable_mod_frame<-data.frame(Variable=(summary(owners_affordable_mod)$amce)$Level,
                                        Coefficient = (summary(owners_affordable_mod)$amce)$Estimate,
                                        SE=(summary(owners_affordable_mod)$amce)$'Std. Err',
                                        modelName="Affordable")
ownersPriceFrame<-data.frame(rbind(owners_luxury_mod_frame, owners_affordable_mod_frame))
ownersPriceFrame<-subset(ownersPriceFrame, Variable=="1/8 mile (2 minute walk)"|Variable=="1/2 mile (10 minute walk)"|Variable=="1 mile (20 minute walk)")
ownersPriceFrameIntercepts<-data.frame(Variable=c("2 miles (40 minute walk)", "2 miles (40 minute walk)") ,Coefficient=c(0,0), SE=c(0,0), modelName=c("Market Rate", "Affordable"))
ownersPriceFrame<-data.frame(rbind(ownersPriceFrame,ownersPriceFrameIntercepts))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
ownersPriceFrame$Variable <- factor(ownersPriceFrame$Variable, levels = c("1/8 mile (2 minute walk)","1/2 mile (10 minute walk)", "1 mile (20 minute walk)", "2 miles (40 minute walk)"))

# Plot ggplot. 

owners_price_nimby<-ggplot(ownersPriceFrame, aes(colour=modelName, shape=modelName))+ scale_y_continuous(limits = c(-.20, .20))
owners_price_nimby<-owners_price_nimby+theme_bw()+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)
owners_price_nimby<-owners_price_nimby+geom_linerange(aes(x=Variable, ymin=Coefficient-SE*interval1, 
                                                          ymax=Coefficient+SE*interval1), lwd=1, position=position_dodge(width=1/2))
owners_price_nimby<-owners_price_nimby+geom_pointrange(aes(x=Variable, y=Coefficient, ymin=Coefficient-SE*interval2,
                                                           ymax=Coefficient+SE*interval2), lwd=1/2,
                                                       position=position_dodge(width=1/2), fill="WHITE")
owners_price_nimby<-owners_price_nimby+coord_flip()+labs(y="Change in Probability Building Preferred")
owners_price_nimby<-owners_price_nimby+theme(legend.title=element_blank(),axis.title.y=element_blank())+ theme(aspect.ratio = .5)
owners_price_nimby<-owners_price_nimby+theme(plot.margin=unit(c(0,0,0,0),"mm"))+ggtitle("Homeowners, Proximity by Affordability") + guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))

```

```{r Figure 3 print, echo = FALSE}

print(owners_price_nimby)

```

### Figure 3. Supplement

```{r Supplemetary Figure 3 Code, include = FALSE, cache = TRUE}
# Supplmentary Figure 3. Homeowners Support for Supply Citywide, Average ZIP Rent ####
quantile(socpoc$zri, probs=seq(0,1,.2), na.rm=T)
zri_city_values<-c(0,1204,1526,1958,2488,13000)

est2<-rep(NA, length(zri_city_values))
se2<-rep(NA, length(zri_city_values))

for(i in 1:5){
  section<-subset(owners, zri>zri_city_values[i] & zri<=zri_city_values[i+1])
  est2[i]<-mean(section$supply_dummy,na.rm=T)
  se2[i]<-sqrt((est2[i]*(1-est2[i]))/nrow(section))
}

mod2ests<-as.data.frame(cbind(zri_city_values,est2,se2))
mod2ests$uCI<-est2+se2*1.96
mod2ests$lCI<-est2-se2*1.96

mod2estimates<-mod2ests[1:5,]
colnames(mod2estimates)<-c("Rent","Estimate", "StdErr", "UpperCI", "LowerCI")
mod2estimates$Quintile<-c(1,2,3,4,5)
mod2estimates
mod2estimates$Cost<-factor(c("Least Expensive","2nd","3rd","4th","Most Expensive"))
levels(mod2estimates$Cost)
pd <- position_dodge(0.1)
mod2estimates$Cost <- factor(mod2estimates$Cost, levels = c("Least Expensive","2nd","3rd","4th","Most Expensive"))
owners_zip_supply<-ggplot(mod2estimates, aes(x=Cost, y=Estimate))+scale_y_continuous(limits = c(0, 1))+coord_flip()+
  geom_errorbar(aes(ymin=LowerCI, ymax=UpperCI), width=.1, position=pd) +
  geom_point(position=pd)+ggtitle("Homeowners Support for Supply Citywide, by Average ZIP Rent")+
  labs(x = "Average ZIP Rent (Quintiles)", y="Support for Supply (%)")+ theme(aspect.ratio=.5)+
  theme_bw()+scale_fill_grey()





```

```{r Print Supplementary Figure 3, echo = FALSE}
print(owners_zip_supply)
```

### Figure 4 Effect of Proximity on Renters by Affordability of Proposed Housing

```{r Figure 4, cache = TRUE, echo = FALSE}
# FIGURE 4. Renters, Proximity by Affordability ####
renters_luxury_mod<-amce(select ~ distance  + community + height + site + tenant + units,
                         data= renters_lux , cluster=T,  respondent.id = "CaseID")
renters_affordable_mod<-amce(select ~ distance  + community + height + site + tenant + units,
                             data=renters_aff, cluster=T,  respondent.id = "CaseID")
renters_luxury_mod_frame<-data.frame(Variable=(summary(renters_luxury_mod)$amce)$Level,
                                     Coefficient = (summary(renters_luxury_mod)$amce)$Estimate,
                                     SE=(summary(renters_luxury_mod)$amce)$'Std. Err',
                                     modelName="Market Rate")
renters_affordable_mod_frame<-data.frame(Variable=(summary(renters_affordable_mod)$amce)$Level,
                                         Coefficient = (summary(renters_affordable_mod)$amce)$Estimate,
                                         SE=(summary(renters_affordable_mod)$amce)$'Std. Err',
                                         modelName="Affordable")
rentersPriceFrame<-data.frame(rbind(renters_luxury_mod_frame, renters_affordable_mod_frame))
rentersPriceFrame<-subset(rentersPriceFrame, Variable=="1/8 mile (2 minute walk)"|Variable=="1/2 mile (10 minute walk)"|Variable=="1 mile (20 minute walk)")
rentersPriceFrameIntercepts<-data.frame(Variable=c("2 miles (40 minute walk)", "2 miles (40 minute walk)") ,Coefficient=c(0,0), SE=c(0,0), modelName=c("Market Rate", "Affordable"))
rentersPriceFrame<-data.frame(rbind(rentersPriceFrame,rentersPriceFrameIntercepts))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
rentersPriceFrame$Variable <- factor(rentersPriceFrame$Variable, levels = c("1/8 mile (2 minute walk)","1/2 mile (10 minute walk)", "1 mile (20 minute walk)", "2 miles (40 minute walk)"))
renters_price_nimby<-ggplot(rentersPriceFrame, aes(colour=modelName, shape=modelName)) + scale_y_continuous(limits = c(-.20, .20))
renters_price_nimby<-renters_price_nimby+theme_bw()+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)
renters_price_nimby<-renters_price_nimby+geom_linerange(aes(x=Variable, ymin=Coefficient-SE*interval1, 
                                                            ymax=Coefficient+SE*interval1), lwd=1, position=position_dodge(width=1/2))
renters_price_nimby<-renters_price_nimby+geom_pointrange(aes(x=Variable, y=Coefficient, ymin=Coefficient-SE*interval2,
                                                             ymax=Coefficient+SE*interval2), lwd=1/2,
                                                         position=position_dodge(width=1/2), fill="WHITE")
renters_price_nimby<-renters_price_nimby+coord_flip()+ labs(y="Change in Probability Building Preferred")
renters_price_nimby<-renters_price_nimby+theme(legend.title=element_blank(), axis.title.y=element_blank())+ theme(aspect.ratio = .5)
renters_price_nimby<-renters_price_nimby+theme(plot.margin=unit(c(0,0,0,0),"mm")) +ggtitle("Renters, Proximity by Affordability")+ guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))


print(renters_price_nimby)

```

### Figure 5 Effect of Proximity on Renters by Affordability of Proposed Housing, Grouped by Average Rent Citywide. Displayed Effect is Shift from Two Miles Away (Baseline) to an Eighth of a Mile Away. Quintile Cutpoints for Average Rent by City at $1,217, $1,480, $1,936, and $2,247

```{r Figure 5 code, cache = TRUE, include = FALSE}

# FIGURE 5, Renters, Nimby by Affordability, Quintile City####

quantile(conjoint4$zri_city, probs=seq(0,1,.1), na.rm=T) # define quintiles

zri_city_values<-c(0,1217,1480,1936,2427,7344)
est1<-rep(NA, length(zri_city_values))
se1<-rep(NA, length(zri_city_values))
for(i in 1:5){
  mod1<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(renters, zri_city>zri_city_values[i] & zri_city<=zri_city_values[i+1]&luxury==1), cluster=T, respondent.id = "CaseID")
  est1[i]<-summary(mod1)$amce[5,3]
  se1[i]<-summary(mod1)$amce[5,4]
}
mod1ests<-as.data.frame(cbind(zri_city_values,est1,se1))
mod1ests$uCI<-est1+se1*1.96
mod1ests$lCI<-est1-se1*1.96
est2<-rep(NA, length(zri_city_values))
se2<-rep(NA, length(zri_city_values))
for(i in 1:5){
  mod2<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(renters, zri_city>zri_city_values[i] & zri_city<=zri_city_values[i+1]&luxury==0), cluster=T, respondent.id = "CaseID")
  est2[i]<-summary(mod2)$amce[5,3]
  se2[i]<-summary(mod2)$amce[5,4]
}
mod2ests<-as.data.frame(cbind(zri_city_values,est2,se2))
mod2ests$uCI<-est2+se2*1.96
mod2ests$lCI<-est2-se2*1.96
#combine data
mod1<-mod1ests[-6,]
mod1$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod1$modelName<-"Market Rate"
names(mod1)<-c("zri","est","se","uci","lci","Quintile","modelName")
mod2<-mod2ests[-6,]
mod2$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod2$modelName<-"Affordable"
names(mod2)<-c("zri","est","se","uci","lci","Quintile","modelName")
modFrame<-data.frame(rbind(mod1,mod2))
modFrame$Quintile <- factor(modFrame$Quintile, levels = c("Least Expensive", "2nd","3rd", "4th", "Most Expensive"))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
modFrame
modFrame$modelName<-factor(modFrame$modelName, levels=c("Market Rate","Affordable"))
renters_type_nimby<-ggplot(modFrame, aes(colour=modelName, shape=modelName))+ scale_y_continuous(limits = c(-.25, .25))
renters_type_nimby<-renters_type_nimby+theme_bw()+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)
renters_type_nimby<-renters_type_nimby+geom_linerange(aes(x=Quintile, ymin=est-se*interval1, 
                                                          ymax=est+se*interval1), lwd=1, position=position_dodge(width=1/2))
#+scale_color_manual(values=c('#F8766D', '#00BFC4'))

renters_type_nimby<-renters_type_nimby+geom_pointrange(aes(x=Quintile, y=est, ymin=est-se*interval2,
                                                           ymax=est+se*interval2), lwd=1/2,
                                                       position=position_dodge(width=1/2),  fill="WHITE")
renters_type_nimby<-renters_type_nimby+coord_flip()+ labs(y="Change in Probability Building Preferred",x="Average Rent by City (Quintiles)")
renters_type_nimby<-renters_type_nimby+theme(legend.title=element_blank()) + theme(aspect.ratio = .5)
renters_type_nimby<-renters_type_nimby+theme(plot.margin=unit(c(0,0,0,0),"mm"))+ ggtitle("Renters, Proximity by Affordability and Average Rent by City") +guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))


```

```{r Print Figure 5, echo = FALSE}
print(renters_type_nimby)
```

### Figure 6. Renter Support for a 10% Increase in Their City/Town’s Housing Supply, by Average Rent Citywide

```{r Figure 6, include = FALSE, cache=TRUE}

quantile(socpoc$zri_city, probs=seq(0,1,.2), na.rm=T)
zri_city_values<-c(0,1217,1480,1936,2427,7344)
est1<-rep(NA, length(zri_city_values))
se1<-rep(NA, length(zri_city_values))

for(i in 1:5){
  section<-subset(renters, zri_city>zri_city_values[i] & zri_city<=zri_city_values[i+1])
  est1[i]<-mean(section$supply_dummy,na.rm=T)
  se1[i]<-sqrt((est1[i]*(1-est1[i]))/nrow(section))
}

mod1ests<-as.data.frame(cbind(zri_city_values,est1,se1))
mod1ests$uCI<-est1+se1*1.96
mod1ests$lCI<-est1-se1*1.96

mod1estimates<-mod1ests[1:5,]
colnames(mod1estimates)<-c("Rent","Estimate", "StdErr", "UpperCI", "LowerCI")
mod1estimates$Quintile<-c(1,2,3,4,5)
mod1estimates
mod1estimates$Cost<-factor(c("Least Expensive","2nd","3rd","4th","Most Expensive"))
levels(mod1estimates$Cost)
pd <- position_dodge(0.1)
mod1estimates$Cost <- factor(mod1estimates$Cost, levels = c("Least Expensive","2nd","3rd","4th","Most Expensive"))
mod1estimates
renter_city_supply<-ggplot(mod1estimates, aes(x=Cost, y=Estimate))+scale_y_continuous(limits = c(0, 1))+coord_flip()+
  geom_errorbar(aes(ymin=LowerCI, ymax=UpperCI), width=.1, position=pd) +
  geom_point(position=pd)+  labs(x = "Average City Rent (Quintiles)", y="Support for Supply (%)")+ggtitle("Renters Support for Supply Citywide, by Average Rent") + theme(aspect.ratio = .5)+
  theme_bw()+scale_fill_grey()

```
```{r Print Figure 6, echo = FALSE}
print(renter_city_supply)
```

### Figure 7. FIGURE 7. Effect of Proximity on Renters Toward Market-Rate Housing by Attitude Toward Housing Prices Citywide

```{r Figure 7 Code, include = FALSE, cache = TRUE}

# FIGURE 7, Renters, nimby by price anxiety ####

renters_city_low_mod<-amce(select ~ distance  + community + height + site + tenant + units,
                           data=subset(renters_lux, city_interest<0) , cluster=T,  respondent.id = "CaseID")
renters_city_high_mod<-amce(select ~ distance  + community + height + site + tenant + units,
                            data=subset(renters_lux, city_interest>=0), cluster=T,  respondent.id = "CaseID")
renters_city_low_mod_frame<-data.frame(Variable=(summary(renters_city_low_mod)$amce)$Level,
                                       Coefficient = (summary(renters_city_low_mod)$amce)$Estimate,
                                       SE=(summary(renters_city_low_mod)$amce)$'Std. Err',
                                       modelName="Price Anxious")
renters_city_high_mod_frame<-data.frame(Variable=(summary(renters_city_high_mod)$amce)$Level,
                                        Coefficient = (summary(renters_city_high_mod)$amce)$Estimate,
                                        SE=(summary(renters_city_high_mod)$amce)$'Std. Err',
                                        modelName="Price Neutral")
rentersCityFrame<-data.frame(rbind(renters_city_low_mod_frame, renters_city_high_mod_frame))
rentersCityFrame<-subset(rentersCityFrame, Variable=="1/8 mile (2 minute walk)"|Variable=="1/2 mile (10 minute walk)"|Variable=="1 mile (20 minute walk)")
rentersCityFrameIntercepts<-data.frame(Variable=c("2 miles (40 minute walk)", "2 miles (40 minute walk)") ,Coefficient=c(0,0), SE=c(0,0), modelName=c("Price Anxious", "Price Neutral"))
rentersCityFrame<-data.frame(rbind(rentersCityFrame,rentersCityFrameIntercepts))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
rentersCityFrame$Variable <- factor(rentersCityFrame$Variable, levels = c("1/8 mile (2 minute walk)","1/2 mile (10 minute walk)", "1 mile (20 minute walk)", "2 miles (40 minute walk)"))
renters_anxious_nimby<-ggplot(rentersCityFrame, aes(colour=modelName, shape=modelName))+ scale_y_continuous(limits = c(-.25, .25))
renters_anxious_nimby<-renters_anxious_nimby+theme_bw()+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)+scale_shape_manual(values=c(4,5))
#+ scale_color_manual(values=c('#990099','#33CC00'))
renters_anxious_nimby<-renters_anxious_nimby+geom_linerange(aes(x=Variable, ymin=Coefficient-SE*interval1, 
                                                                ymax=Coefficient+SE*interval1), lwd=1, position=position_dodge(width=1/2))
renters_anxious_nimby<-renters_anxious_nimby+geom_pointrange(aes(x=Variable, y=Coefficient, ymin=Coefficient-SE*interval2,
                                                                 ymax=Coefficient+SE*interval2), lwd=1/2,
                                                             position=position_dodge(width=1/2), fill="WHITE")
renters_anxious_nimby<-renters_anxious_nimby+coord_flip()+ labs(y="Change in Probability Building Preferred")
renters_anxious_nimby<-renters_anxious_nimby+theme(legend.title=element_blank(),axis.title.y=element_blank())+theme(aspect.ratio = .5)
renters_anxious_nimby<-renters_anxious_nimby+theme(plot.margin=unit(c(0,0,0,0),"mm")) + ggtitle("Renters, Proximity by Price Anxiety (Market Rate)")+ theme(aspect.ratio = .5)+ guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))
```

```{r Figure 7 print, echo = FALSE}

print(renters_anxious_nimby)

```

# APPENDIX

## A San Francisco

### Table A.1. Descriptive Statistics, San Francisco Sample

### Table A.2. Proposition Vote Share, San Francisco Sample

### Table A.3. Policy Proposals, San Francisco Sample

```{r Table A.3 Code, include = FALSE, cache = TRUE, results = 'asis'}

# Table A.3: Policy Proposals, SF

# Run Regressions

simple_control<-(lm(ten_plan_dummy ~ ownership_dummy, final)); summary(simple_control)

simple_control_se<-sqrt(diag(vcovHC(simple_control, type="HC1")))

full_control<-(lm(ten_plan_dummy ~ ownership_dummy  +  scale(ideology_num) +scale(income_num) + white_dummy  + age+ gender_dummy , control)); summary(full_control)
full_control_se<-sqrt(diag(vcovHC(full_control, type="HC1")))

#Supplementary Data
stargazer(simple_control, full_control, title="Ten Percent Supply Increase, San Francisco",  label="ten_pct_dummy", 
          dep.var.labels=c("Support Supply Increase"), dep.var.labels.include = F, dev.var.caption="",
          column.labels=c("Bivariate", "Full"),
          covariate.labels=c("Homeownership","Ideology","Income, Log","White, Non-Hispanic","Age","Male"),
          omit.stat=c("ser","f"), digits=2, align=T,
          initial.zero = F, font.size="small", star.cutoffs = NA, omit.table.layout="n",
          se=list(simple_control_se, full_control_se), no.space=T, omit=c("name"))


#model ban
simple_prop_i_ban<-(lm(prop_i_ban_dummy ~ ownership_dummy  , final)); summary(simple_prop_i_ban)
simple_prop_i_ban_se<-sqrt(diag(vcovHC(simple_prop_i_ban, type="HC1")))

full_prop_i_ban<-(lm(prop_i_ban_dummy ~ ownership_dummy  +  scale(ideology_num) +scale(income_num) + white_dummy  + age+ gender_dummy , final)); summary(full_prop_i_ban)
full_prop_i_ban_se<-sqrt(diag(vcovHC(full_prop_i_ban, type="HC1")))

#Table. Ban support
stargazer(simple_prop_i_ban, full_prop_i_ban, title="Neighborhood Ban, San Francisco",  label="prop_i_ban_dummy",
          dep.var.labels=c("Support Supply Increase"), dep.var.labels.include = F, dev.var.caption="",
          column.labels=c("Bivariate", "Full"),
          covariate.labels=c("Homeownership","Ideology","Income, Log","White, Non-Hispanic","Age","Male"),
          omit.stat=c("ser","f"), digits=2, align=T,
          initial.zero = F, font.size="small", star.cutoffs = NA, omit.table.layout="n",
          se=list(simple_prop_i_ban_se, full_prop_i_ban_se), no.space=T, omit=c("name"))
```

```{r Figure A.3 print, echo = FALSE, results = 'asis'}
# Table. Combine these two tables

stargazer(simple_control, full_control, simple_prop_i_ban, full_prop_i_ban, title="Policy Proposals, San Francisco Sample",  label="sf_policies",
          dep.var.labels.include = F, dev.var.caption="",
          column.labels=c("10 Pct Supply", "NIMBY Ban Proposal" ), column.separate = c(2, 2),
          covariate.labels=c("Homeownership","Ideology","Income, Log","White, Non-Hispanic","Age","Male"),
          omit.stat=c("ser","f"), digits=2, align=T, type="html",
          initial.zero = F, font.size="small", star.cutoffs = NA, omit.table.layout="n",
          se=list(simple_control_se, full_control_se, simple_prop_i_ban_se, full_prop_i_ban_se), no.space=T )


```

### Figure A.1.  Effect of Proximity on Recontacted San Francisco Renters Toward Market-Rate Housing by Support for Hypothetical Ban on Market-Rate Housing in own Neighborhood

```{r Figure A.1 Code, include = FALSE, cache = TRUE}
conjoint_sf<-read.csv("conjointSFAPSR.csv")

conjoint_sf$distance <- factor(conjoint_sf$distance,levels= c("2 miles (40 minute walk)", "1 mile (20 minute walk)", "1/2 mile (10 minute walk)",
                                                              "1/8 mile (2 minute walk)"))
conjoint_sf$community <- factor(conjoint_sf$community,levels= c("No opinion", "Support the building", "Oppose the building"))
conjoint_sf$affordable <- factor(conjoint_sf$affordable,levels= c("None of the units", "One-quarter of the units", "Half of the units", "All of the units"))
conjoint_sf$height <- factor(conjoint_sf$height,levels= c("2 stories", "3 stories", "6 stories", "12 stories"))
conjoint_sf$site <- factor(conjoint_sf$site, levels=c("Empty building","Parking lot","Open field","Historically-designated building"))

#add indicators 
conjoint_sf$city_interest_low<-as.factor(ifelse(conjoint_sf$city_interest<0,1,0))
conjoint_sf$prop_i_ban_dummy<-as.factor(ifelse(conjoint_sf$prop_i_ban_dummy==1,1,0))
conjoint_sf$luxury<-as.factor(ifelse(conjoint_sf$affordable=="None of the units",1,0))

#subgroups
owners<-subset(conjoint_sf, own==1)
renters<-subset(conjoint_sf, own==0)

owners_aff<-subset(owners, luxury==0)
owners_lux<-subset(owners, luxury==1)

renters_aff<-subset(renters, luxury==0)
renters_lux<-subset(renters, luxury==1)

# Figure A.1. Recontacted Conjoint San Francisco Sample ####
renters_prop_i_yes_mod<-amce(selected ~ distance  + community + height + site + tenant + units,
                             data=subset(renters_lux, prop_i_ban_dummy==1&supply_dummy==1),cluster=T,  respondent.id = "respondent")
renters_prop_i_no_mod<-amce(selected ~ distance  + community + height + site + tenant + units,
                            data=subset(renters_lux, prop_i_ban_dummy==0&supply_dummy==1), cluster=T,  respondent.id = "respondent")
renters_prop_i_yes_mod_frame<-data.frame(Variable=(summary(renters_prop_i_yes_mod)$amce)$Level,
                                         Coefficient = (summary(renters_prop_i_yes_mod)$amce)$Estimate,
                                         SE=(summary(renters_prop_i_yes_mod)$amce)$'Std. Err',
                                         modelName="Supporters")
renters_prop_i_no_mod_frame<-data.frame(Variable=(summary(renters_prop_i_no_mod)$amce)$Level,
                                        Coefficient = (summary(renters_prop_i_no_mod)$amce)$Estimate,
                                        SE=(summary(renters_prop_i_no_mod)$amce)$'Std. Err',
                                        modelName="Opponents")
rentersPropIFrame<-data.frame(rbind(renters_prop_i_yes_mod_frame, renters_prop_i_no_mod_frame))
rentersPropIFrame<-subset(rentersPropIFrame, Variable=="1/8 mile (2 minute walk)"|Variable=="1/2 mile (10 minute walk)"|Variable=="1 mile (20 minute walk)")
rentersPropIFrameIntercepts<-data.frame(Variable=c("2 miles (40 minute walk)", "2 miles (40 minute walk)") ,Coefficient=c(0,0), SE=c(0,0), modelName=c("Supporters", "Opponents"))
rentersPropIFrame<-data.frame(rbind(rentersPropIFrame,rentersPropIFrameIntercepts))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
rentersPropIFrame$Variable <- factor(rentersPropIFrame$Variable, levels = c("1/8 mile (2 minute walk)","1/2 mile (10 minute walk)", "1 mile (20 minute walk)", "2 miles (40 minute walk)"))
rentersPropIFrame
rentersPropINimby<-ggplot(rentersPropIFrame, aes(colour=modelName, shape=modelName))+scale_shape_manual(values=c(4,5))
#+  scale_color_manual(values=c('#FF9933','#3399FF'))
rentersPropINimby<-rentersPropINimby+theme_bw()+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)
rentersPropINimby<-rentersPropINimby+geom_linerange(aes(x=Variable, ymin=Coefficient-SE*interval1, 
                                                        ymax=Coefficient+SE*interval1), lwd=1, position=position_dodge(width=1/2))
rentersPropINimby<-rentersPropINimby+geom_pointrange(aes(x=Variable, y=Coefficient, ymin=Coefficient-SE*interval2,
                                                         ymax=Coefficient+SE*interval2), lwd=1/2,
                                                     position=position_dodge(width=1/2), fill="WHITE")
rentersPropINimby<-rentersPropINimby+coord_flip()+labs(y="Change in Probability Building Preferred")
rentersPropINimby<-rentersPropINimby+theme(legend.title=element_blank(),axis.title.y=element_blank())+ theme(aspect.ratio = .5)
rentersPropINimby<-rentersPropINimby+theme(plot.margin=unit(c(0,0,0,0),"mm")) + ggtitle("Renters, Proximity and Ban Support (Market Rate)") + guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))


```

```{r Figure A.1 print, echo = FALSE}

print(rentersPropINimby)

```

## NATIONAL SURVEY NON-CONJOINT

### Table B.1. Descriptive Statistics, National Sample

### Table B.2. Support for 10% Supply Increase

```{r Table B.2, cache = TRUE, echo = FALSE, results = 'asis'}

# Table B.2 Support for 10% Supply Increase

# Run Regressionss

# Bivariate

supply_simple<-(lm(supply_dummy ~ own, socpoc))
supply_simple_se<-sqrt(diag(vcovHC(supply_simple, type="HC1")))

# Full

supply_full<-(lm(supply_dummy ~ own +scale(ideology)+scale(log(income)) + whitenh  +age + male, subset(socpoc)))
supply_full_se<-sqrt(diag(vcovHC(supply_full, type="HC1")))

# Full w/ fixed effects

supply_full_fe<-(lm(supply_dummy ~  own +scale(ideology)+ scale(log(income))+ whitenh  + age + male +factor(name), socpoc))
supply_full_fe_se<-sqrt(diag(vcovHC(supply_full_fe, type="HC1")))

# Create Regression Table

stargazer(supply_simple,  supply_full , supply_full_fe, title="Support for 10 Percent Supply Increase", label="supply_7",
          dep.var.labels=c("Support Supply Increase"),dep.var.labels.include = F, dep.var.caption = "",
          column.labels=c("Bivariate","Full","Full with Fixed Effects"),
          covariate.labels=c("Homeownership","Ideology","Income, Log","White, Non-Hispanic","Age","Male"),
          omit.stat = c("ser", "f"), digits=2, align=T, type="html",
          initial.zero = F,  font.size = "small", star.cutoffs = NA, omit.table.layout = "n",
          se=list(supply_simple_se, supply_full_se, supply_full_fe_se), no.space=T,omit=c("name"))

```

### Table B.3. Support for 10% Supply Increase—Seven-Point Scale

```{r Table B.3, cache = TRUE, echo = FALSE, results = 'asis'}

# Table B.3. Support for 10 Percent Supply Increase - 7 Point Scale ####

# Run Regressions

# Bivariate

supply_7_simple<-(lm(city_supply ~ own, socpoc))
supply_7_simple_se<-sqrt(diag(vcovHC(supply_7_simple, type="HC1")))

# Full

supply_7_full<-(lm(city_supply ~ own +scale(ideology)+scale(log(income)) + whitenh  +age + male, subset(socpoc)))
supply_7_full_se<-sqrt(diag(vcovHC(supply_7_full, type="HC1")))

# Full w/ fixed effects

supply_7_full_fe<-(lm(city_supply ~  own +scale(ideology)+ scale(log(income))+ whitenh  + age + male +factor(name), socpoc))
supply_7_full_fe_se<-sqrt(diag(vcovHC(supply_7_full_fe, type="HC1")))

# Create Table

stargazer(supply_7_simple,  supply_7_full , supply_7_full_fe, title="Support for 10 Percent Supply Increase - 7 Point Scale", label="supply_7",
          dep.var.labels=c("Support Supply Increase"),dep.var.labels.include = F, dep.var.caption = "",
          column.labels=c("Bivariate","Full","Full with Fixed Effects"),
          covariate.labels=c("Homeownership","Ideology","Income, Log","White, Non-Hispanic","Age","Male"),
          omit.stat = c("ser", "f"), digits=2, align=T, type="html",
          initial.zero = F,  font.size = "small", star.cutoffs = NA, omit.table.layout = "n",
          se=list(supply_7_simple_se, supply_7_full_se, supply_7_full_fe_se), no.space=T,omit=c("name"))

```

### Table B.4. Support for Ban on Neighborhood Development

```{r Table B.4, echo = FALSE, cache = TRUE, results = 'asis'}

# Table B.4. Support for Neighborhood Ban ####

# bivariate
ban_simple<-(lm(ban_dummy ~ own, socpoc))
ban_simple_se<-sqrt(diag(vcovHC(ban_simple, type="HC1")))

# full

ban_full<-(lm(ban_dummy ~ own +scale(ideology)+scale(log(income)) + whitenh  +age + male, socpoc))
ban_full_se<-sqrt(diag(vcovHC(ban_full, type="HC1")))

#full w/ fixed effects
ban_full_fe<-(lm(ban_dummy ~  own +scale(ideology)+ scale(log(income))+ whitenh  + age + male +factor(name), socpoc))
ban_full_fe_se<-sqrt(diag(vcovHC(ban_full_fe, type="HC1")))

# Table
stargazer(ban_simple,  ban_full , ban_full_fe, title="Support for Ban on Neighborhood Development", label="ban_dummy",
          dep.var.labels=c("Support NIMBY Ban"),dep.var.labels.include = F, dep.var.caption = "",
          column.labels=c("Bivariate","Full","Full with Fixed Effects"),
          covariate.labels=c("Homeownership","Ideology","Income, Log","White, Non-Hispanic","Age","Male"),
          omit.stat = c("ser", "f"), digits=2, align=T, type="html",
          initial.zero = F,  font.size = "small",star.cutoffs = NA, omit.table.layout = "n",
          se=list(ban_simple_se, ban_full_se, ban_full_fe_se), no.space=T, omit=c("name"))

```

### Table B.5. Support for Ban on Neighborhood Development—Seven-Point Scale

```{r Table B.5, cache = TRUE, echo = FALSE, results = 'asis'}

# Table B.5. Support for Neighborhood Ban 7 point scale ####

#simple

ban_simple<-(lm(neighborhood_ban ~ own, socpoc))
ban_simple_se<-sqrt(diag(vcovHC(ban_simple, type="HC1")))

# full

ban_full<-(lm(neighborhood_ban ~ own +scale(ideology)+scale(log(income)) + whitenh  +age + male, socpoc))
ban_full_se<-sqrt(diag(vcovHC(ban_full, type="HC1")))

#full w/ fixed effects

ban_full_fe<-(lm(neighborhood_ban ~  own +scale(ideology)+ scale(log(income))+ whitenh  + age + male +factor(name), socpoc))
ban_full_fe_se<-sqrt(diag(vcovHC(ban_full_fe, type="HC1")))

# Table
stargazer(ban_simple,  ban_full , ban_full_fe, title="Support for Ban on Neighborhood Development - 7 Point Scale", label="neighborhood_ban_7",
          dep.var.labels=c("Support NIMBY Ban"),dep.var.labels.include = F, dep.var.caption = "",
          column.labels=c("Bivariate","Full","Full with Fixed Effects"),
          covariate.labels=c("Homeownership","Ideology","Income, Log","White, Non-Hispanic","Age","Male"),
          omit.stat = c("ser", "f"), digits=2, align=T, type="html",
          initial.zero = F,  font.size = "small",star.cutoffs = NA, omit.table.layout = "n",
          se=list(ban_simple_se, ban_full_se, ban_full_fe_se), no.space=T, omit=c("name"))
```





## C Conjoint Results

### Figure C.1. Homeowner Spatial Sensitivity by Household Income. Above Median Income > $80,000, Below Median Income ≤ $80,000

```{r Figure C.1 code, include = FALSE, cache = TRUE}

# Figure C.1. Homeowner Proximity by Income ####

summary(owners$income) #median==80,000
owners_liberal<-amce(select ~ distance + affordable + community + height + site + tenant + units,
                     data=subset(owners, income>80000), cluster=T,  respondent.id = "CaseID")
owners_conservatives<-amce(select ~ distance + affordable + community + height + site + tenant + units,
                           data=subset(owners, income<=80000), cluster=T,  respondent.id = "CaseID")
owners_liberal_frame<-data.frame(Variable=(summary(owners_liberal)$amce)$Level,
                                 Coefficient = (summary(owners_liberal)$amce)$Estimate,
                                 SE=(summary(owners_liberal)$amce)$'Std. Err',
                                 modelName="Below Median Income")
owners_liberal_frame
owners_conservatives_frame<-data.frame(Variable=(summary(owners_conservatives)$amce)$Level,
                                       Coefficient = (summary(owners_conservatives)$amce)$Estimate,
                                       SE=(summary(owners_conservatives)$amce)$'Std. Err',
                                       modelName="Above Median Income")
ideologyFrame<-data.frame(rbind(owners_liberal_frame, owners_conservatives_frame))
ideologyFrame<-subset(ideologyFrame, Variable=="1/8 mile (2 minute walk)"|Variable=="1/2 mile (10 minute walk)"|Variable=="1 mile (20 minute walk)")
ideologyFrameIntercepts<-data.frame(Variable=c("2 miles (40 minute walk)", "2 miles (40 minute walk)") ,Coefficient=c(0,0), SE=c(0,0), modelName=c("Below Median Income", "Above Median Income"))
ideologyFrame<-data.frame(rbind(ideologyFrame,ideologyFrameIntercepts))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
ideologyFrame$Variable <- factor(ideologyFrame$Variable, levels = c("1/8 mile (2 minute walk)","1/2 mile (10 minute walk)", "1 mile (20 minute walk)", "2 miles (40 minute walk)"))
ideology_affordable<-ggplot(ideologyFrame, aes(colour=modelName, shape=modelName))+ scale_y_continuous(limits = c(-.25, .25))
ideology_affordable<-ideology_affordable+theme_bw()+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)
ideology_affordable<-ideology_affordable+geom_linerange(aes(x=Variable, ymin=Coefficient-SE*interval1, 
                                                            ymax=Coefficient+SE*interval1), lwd=1, position=position_dodge(width=1/2))
ideology_affordable<-ideology_affordable+geom_pointrange(aes(x=Variable, y=Coefficient, ymin=Coefficient-SE*interval2,
                                                             ymax=Coefficient+SE*interval2), lwd=1/2,
                                                         position=position_dodge(width=1/2),  fill="WHITE")
ideology_affordable<-ideology_affordable+coord_flip()+ labs(y="Change in Probability Building Preferred")
ideology_affordable<-ideology_affordable+theme(legend.title=element_blank(),axis.title.y=element_blank())+ theme(aspect.ratio = .5)
ideology_affordable<-ideology_affordable+theme(plot.margin=unit(c(0,0,0,0),"mm"))+ggtitle("Homeowners, Proximity by Income")+guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))
```

```{r Figure C.1 print, echo = FALSE}

print(ideology_affordable)

```

### Figure C.2. Homeowner Spatial Sensitivity by Ideology

```{r Figure C.2 code, include = FALSE, cache = TRUE}

# Figure C.2 Homeowner Proximity by Ideology ####
owners_liberal<-amce(select ~ distance + affordable  + community + height + site + tenant + units,
                     data=subset(owners_aff, ideology>4), cluster=T,  respondent.id = "CaseID")
owners_conservatives<-amce(select ~ distance + affordable  + community + height + site + tenant + units,
                           data=subset(owners_aff, ideology<4), cluster=T,  respondent.id = "CaseID")
owners_liberal_frame<-data.frame(Variable=(summary(owners_liberal)$amce)$Level,
                                 Coefficient = (summary(owners_liberal)$amce)$Estimate,
                                 SE=(summary(owners_liberal)$amce)$'Std. Err',
                                 modelName="Liberals")
owners_liberal_frame
owners_conservatives_frame<-data.frame(Variable=(summary(owners_conservatives)$amce)$Level,
                                       Coefficient = (summary(owners_conservatives)$amce)$Estimate,
                                       SE=(summary(owners_conservatives)$amce)$'Std. Err',
                                       modelName="Conservatives")
ideologyFrame<-data.frame(rbind( owners_conservatives_frame,owners_liberal_frame))
ideologyFrame<-subset(ideologyFrame, Variable=="1/8 mile (2 minute walk)"|Variable=="1/2 mile (10 minute walk)"|Variable=="1 mile (20 minute walk)")
ideologyFrameIntercepts<-data.frame(Variable=c("2 miles (40 minute walk)", "2 miles (40 minute walk)") ,Coefficient=c(0,0), SE=c(0,0), modelName=c( "Conservatives", "Liberals"))
ideologyFrame<-data.frame(rbind(ideologyFrame,ideologyFrameIntercepts))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
ideologyFrame$Variable <- factor(ideologyFrame$Variable, levels = c("1/8 mile (2 minute walk)","1/2 mile (10 minute walk)", "1 mile (20 minute walk)", "2 miles (40 minute walk)"))
ideology_affordable<-ggplot(ideologyFrame, aes(colour=modelName, shape=modelName))+ scale_y_continuous(limits = c(-.25, .25))
ideology_affordable<-ideology_affordable+theme_bw()+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)
ideology_affordable<-ideology_affordable+geom_linerange(aes(x=Variable, ymin=Coefficient-SE*interval1, 
                                                            ymax=Coefficient+SE*interval1), lwd=1, position=position_dodge(width=1/2))
ideology_affordable<-ideology_affordable+geom_pointrange(aes(x=Variable, y=Coefficient, ymin=Coefficient-SE*interval2,
                                                             ymax=Coefficient+SE*interval2), lwd=1/2,
                                                         position=position_dodge(width=1/2),  fill="WHITE")
ideology_affordable<-ideology_affordable+coord_flip()+ labs(y="Change in Probability Building Preferred")
ideology_affordable<-ideology_affordable+theme(legend.title=element_blank(),axis.title.y=element_blank())+ theme(aspect.ratio = .5)
ideology_affordable<-ideology_affordable+theme(plot.margin=unit(c(0,0,0,0),"mm"))+ggtitle("Homeowners, Proximity by Ideology")+guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))

```

```{r Figure C2 print, echo = FALSE}

print(ideology_affordable)

```

### Figure C.3. Effect of an Eighth-Mile Away Compared to Baseline of Two Miles Away for Each Level of Affordability, by Homeownership Status

```{r Figure C.3 code, cache = TRUE, include = FALSE}

# Figure C.3 Proximity by Affordability Homeowners and Renters ####

affordable_values<-c("None of the units", "One-quarter of the units", "Half of the units", "All of the units")
est1<-rep(NA, length(affordable_values))
se1<-rep(NA, length(affordable_values))
for(i in 1:4){
  mod1<-amce(select ~ distance + community + height + site + tenant + units,
             data=subset(owners, affordable==affordable_values[i]), cluster=T, respondent.id = "CaseID")
  est1[i]<-summary(mod1)$amce[5,3]
  se1[i]<-summary(mod1)$amce[5,4]
}
mod1ests<-as.data.frame(cbind(affordable_values,est1,se1))
mod1ests$uCI<-est1+se1*1.96
mod1ests$lCI<-est1-se1*1.96

est2<-rep(NA, length(affordable_values))
se2<-rep(NA, length(affordable_values))
for(i in 1:4){
  mod2<-amce(select ~ distance + community + height + site + tenant + units,
             data=subset(renters, affordable==affordable_values[i]), cluster=T, respondent.id = "CaseID")
  est2[i]<-summary(mod2)$amce[5,3]
  se2[i]<-summary(mod2)$amce[5,4]
}
mod2ests<-as.data.frame(cbind(affordable_values,est2,se2))
mod2ests$uCI<-est1+se1*1.96
mod2ests$lCI<-est1-se1*1.96
mod2ests
#combine data

mod1<-mod1ests
class(mod1$est)
mod1$quintle<-c("None of the units", "One-quarter of the units", "Half of the units", "All of the units")
mod1$modelName<-"Homeowners"
names(mod1)<-c("affordability","est","se","uci","lci","Quintile","modelName")
mod2<-mod2ests
mod2$quintle<-c("None of the units", "One-quarter of the units", "Half of the units", "All of the units")
mod2$modelName<-"Renters"
names(mod2)<-c("affordability","est","se","uci","lci","Quintile","modelName")
modFrame<-data.frame(rbind(mod1,mod2))
modFrame$Quintile <- factor(modFrame$Quintile, levels = c("None of the units", "One-quarter of the units", "Half of the units", "All of the units"))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
modFrame$est<-as.numeric(as.character(modFrame$est))
modFrame$se<-as.numeric(as.character(modFrame$se))

modFrame$modelName<-factor(modFrame$modelName, levels=c("Homeowners","Renters"))
modFrame
renters_type_nimby<-ggplot(modFrame, aes(colour=modelName, shape=modelName))+ scale_y_continuous(limits = c(-.2, .2))
renters_type_nimby<-renters_type_nimby+theme_bw()+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)
renters_type_nimby<-renters_type_nimby+geom_linerange(aes(x=Quintile, ymin=est-se*interval1, 
                                                          ymax=est+se*interval1), lwd=1, position=position_dodge(width=1/2))
renters_type_nimby<-renters_type_nimby+geom_pointrange(aes(x=Quintile, y=est, ymin=est-se*interval2,
                                                           ymax=est+se*interval2), lwd=1/2,
                                                       position=position_dodge(width=1/2),  fill="WHITE")
renters_type_nimby<-renters_type_nimby+coord_flip()+ labs(y="Change in Probability Building Preferred",x="Affordability Level")
renters_type_nimby<-renters_type_nimby+theme(legend.title=element_blank())+ theme(aspect.ratio = .5)
renters_type_nimby<-renters_type_nimby+theme(plot.margin=unit(c(0,0,0,0),"mm")) + ggtitle("Proximity by Affordability") + guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))

```

```{r Figure C.3 print, echo = FALSE}

print(renters_type_nimby)

```

### Figure C.4. Renter Spatial Sensitivity toward all Affordability Levels, by Citywide Average Rent

```{r Figure C.4 code, include = FALSE, cache = TRUE}

# Figure C.4 Renters Proximity by each level of affordability, by City ####

quantile(conjoint4$zri_city, probs=seq(0,1,.2), na.rm=T)

zri_values<-c(0,1217,1480,1936,2427,7500)
est1<-rep(NA, length(zri_values))
se1<-rep(NA, length(zri_values))
for(i in 1:5){
  mod1<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(renters, zri_city>zri_values[i] & zri_city<=zri_values[i+1]&affordable=="None of the units"), cluster=T, respondent.id = "CaseID")
  est1[i]<-summary(mod1)$amce[5,3]
  se1[i]<-summary(mod1)$amce[5,4]
}
mod1ests<-as.data.frame(cbind(zri_values,est1,se1))
mod1ests$uCI<-est1+se1*1.96
mod1ests$lCI<-est1-se1*1.96

est2<-rep(NA, length(zri_values))
se2<-rep(NA, length(zri_values))
for(i in 1:5){
  mod2<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(renters, zri_city>zri_values[i] & zri_city<=zri_values[i+1]&affordable=="One-quarter of the units"), cluster=T, respondent.id = "CaseID")
  est2[i]<-summary(mod2)$amce[5,3]
  se2[i]<-summary(mod2)$amce[5,4]
}
mod2ests<-as.data.frame(cbind(zri_values,est2,se2))
mod2ests$uCI<-est2+se2*1.96
mod2ests$lCI<-est2-se2*1.96

est3<-rep(NA, length(zri_values))
se3<-rep(NA, length(zri_values))
for(i in 1:5){
  mod3<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(renters, zri_city>zri_values[i] & zri_city<=zri_values[i+1]&affordable=="Half of the units"), cluster=T, respondent.id = "CaseID")
  est3[i]<-summary(mod3)$amce[5,3]
  se3[i]<-summary(mod3)$amce[5,4]
}
mod3ests<-as.data.frame(cbind(zri_values,est3,se3))
mod3ests$uCI<-est3+se3*1.96
mod3ests$lCI<-est3-se3*1.96

est4<-rep(NA, length(zri_values))
se4<-rep(NA, length(zri_values))
for(i in 1:5){
  mod4<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(renters, zri_city>zri_values[i] & zri_city<=zri_values[i+1]&affordable=="All of the units"), cluster=T, respondent.id = "CaseID")
  est4[i]<-summary(mod4)$amce[5,3]
  se4[i]<-summary(mod4)$amce[5,4]
}
mod4ests<-as.data.frame(cbind(zri_values,est4,se4))
mod4ests$uCI<-est4+se4*1.96
mod4ests$lCI<-est4-se4*1.96

#combine data
mod1<-mod1ests[-6,]
mod1$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod1$modelName<-"None of Units"
names(mod1)<-c("zri","est","se","uci","lci","Quintile","modelName")

mod2<-mod2ests[-6,]
mod2$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod2$modelName<-"Quarter of Units"
names(mod2)<-c("zri","est","se","uci","lci","Quintile","modelName")

mod3<-mod3ests[-6,]
mod3$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod3$modelName<-"Half of Units"
names(mod3)<-c("zri","est","se","uci","lci","Quintile","modelName")

mod4<-mod4ests[-6,]
mod4$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod4$modelName<-"All of Units"
names(mod4)<-c("zri","est","se","uci","lci","Quintile","modelName")

modFrame<-data.frame(rbind(mod1,mod2,mod3,mod4))
modFrame$Quintile <- factor(modFrame$Quintile, levels = c("Least Expensive","2nd","3rd","4th","Most Expensive"))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
modFrame
modFrame$modelName<-factor(modFrame$modelName, levels=c("None of Units","Quarter of Units","Half of Units","All of Units"))
renters_type_nimby<-ggplot(modFrame, aes(colour=modelName, shape=modelName))+ scale_y_continuous(limits = c(-.3, .3))#+ scale_colour_discrete(name="Affordability") +scale_shape_discrete(name="Affordability")
renters_type_nimby<-renters_type_nimby+theme_bw()+theme(legend.title = element_blank())+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)
renters_type_nimby<-renters_type_nimby+geom_linerange(aes(x=Quintile, ymin=est-se*interval1, 
                                                          ymax=est+se*interval1), lwd=1, position=position_dodge(width=1/2))
renters_type_nimby<-renters_type_nimby+geom_pointrange(aes(x=Quintile, y=est, ymin=est-se*interval2,
                                                           ymax=est+se*interval2), lwd=1/2,
                                                       position=position_dodge(width=1/2),  fill="WHITE")
renters_type_nimby<-renters_type_nimby+coord_flip()+ labs(y="Change in Probability Building Preferred",x="Average City Rent (Quintiles)")
renters_type_nimby<-renters_type_nimby+theme(plot.margin=unit(c(0,0,0,0),"mm"))+ggtitle(("Renters, Proximity by Affordability and Average Rent by City"))+guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))

```

```{r Figure C.4 print, echo = FALSE}

print(renters_type_nimby)
```

### Figure C.5. Renter Spatial Sensitivity toward Affordability Levels, by ZIP Code Average Rent

```{r Figure C.5, include = FALSE, cache = TRUE}

# Figure C.5 Renters Proximity by Affordability and Average Rent by ZIP ####

quantile(conjoint4$zri, probs=seq(0,1,.2), na.rm=T)
zri_city_values<-c(0,1204,1526,1959,2488,13000)
est1<-rep(NA, length(zri_city_values))
se1<-rep(NA, length(zri_city_values))
for(i in 1:5){
  mod1<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(renters, zri>zri_city_values[i] & zri<=zri_city_values[i+1]&luxury==1), cluster=T, respondent.id = "CaseID")
  est1[i]<-summary(mod1)$amce[5,3]
  se1[i]<-summary(mod1)$amce[5,4]
}
mod1ests<-as.data.frame(cbind(zri_city_values,est1,se1))
mod1ests$uCI<-est1+se1*1.96
mod1ests$lCI<-est1-se1*1.96
est2<-rep(NA, length(zri_city_values))
se2<-rep(NA, length(zri_city_values))
for(i in 1:5){
  mod2<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(renters, zri>zri_city_values[i] & zri<=zri_city_values[i+1]&luxury==0), cluster=T, respondent.id = "CaseID")
  est2[i]<-summary(mod2)$amce[5,3]
  se2[i]<-summary(mod2)$amce[5,4]
}
mod2ests<-as.data.frame(cbind(zri_city_values,est2,se2))
mod2ests$uCI<-est2+se2*1.96
mod2ests$lCI<-est2-se2*1.96
#combine data
mod1<-mod1ests[-6,]
mod1$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod1$modelName<-"Market Rate"
names(mod1)<-c("zri","est","se","uci","lci","Quintile","modelName")
mod2<-mod2ests[-6,]
mod2$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod2$modelName<-"Affordable"
names(mod2)<-c("zri","est","se","uci","lci","Quintile","modelName")
modFrame<-data.frame(rbind(mod1,mod2))
modFrame$Quintile <- factor(modFrame$Quintile, levels = c("Least Expensive", "2nd","3rd", "4th", "Most Expensive"))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
modFrame
modFrame$modelName<-factor(modFrame$modelName, levels=c("Market Rate","Affordable"))
renters_type_nimby<-ggplot(modFrame, aes(colour=modelName, shape=modelName))+ scale_y_continuous(limits = c(-.25, .25))
renters_type_nimby<-renters_type_nimby+theme_bw()+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)
renters_type_nimby<-renters_type_nimby+geom_linerange(aes(x=Quintile, ymin=est-se*interval1, 
                                                          ymax=est+se*interval1), lwd=1, position=position_dodge(width=1/2))
renters_type_nimby<-renters_type_nimby+geom_pointrange(aes(x=Quintile, y=est, ymin=est-se*interval2,
                                                           ymax=est+se*interval2), lwd=1/2,
                                                       position=position_dodge(width=1/2),  fill="WHITE")
renters_type_nimby<-renters_type_nimby+coord_flip()+ labs(y="Change in Probability Building Preferred",x="Average ZIP Rent (Quintiles)")
renters_type_nimby<-renters_type_nimby+theme(legend.title=element_blank()) + theme(aspect.ratio = .5)
renters_type_nimby<-renters_type_nimby+theme(plot.margin=unit(c(0,0,0,0),"mm"))+ ggtitle("Renters, Proximity by Affordability and Average Rent by ZIP") +guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))

```

```{r Figure C.5 print, echo = FALSE}

print(renters_type_nimby)

```

### Figure C.6. Homeowner Spatial Sensitivity to all Affordability Levels, by Citywide Average Rent

```{r Figure C.6 code, include = FALSE, cache = TRUE}

# Figure C.6 Homeowners Proximity by each level of affordability, by City ####

quantile(conjoint4$zri_city, probs=seq(0,1,.2), na.rm=T)
zri_values<-c(0,1217,1480,1936,2427,7500)
est1<-rep(NA, length(zri_values))
se1<-rep(NA, length(zri_values))
for(i in 1:5){
  mod1<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(owners, zri_city>zri_values[i] & zri_city<zri_values[i+1]&affordable=="None of the units"), cluster=T, respondent.id = "CaseID")
  est1[i]<-summary(mod1)$amce[5,3]
  se1[i]<-summary(mod1)$amce[5,4]
}
mod1ests<-as.data.frame(cbind(zri_values,est1,se1))
mod1ests$uCI<-est1+se1*1.96
mod1ests$lCI<-est1-se1*1.96


est2<-rep(NA, length(zri_values))
se2<-rep(NA, length(zri_values))
for(i in 1:5){
  mod2<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(owners, zri_city>zri_values[i] & zri_city<zri_values[i+1]&affordable=="One-quarter of the units"), cluster=T, respondent.id = "CaseID")
  est2[i]<-summary(mod2)$amce[5,3]
  se2[i]<-summary(mod2)$amce[5,4]
}
mod2ests<-as.data.frame(cbind(zri_values,est2,se2))
mod2ests$uCI<-est2+se2*1.96
mod2ests$lCI<-est2-se2*1.96

est3<-rep(NA, length(zri_values))
se3<-rep(NA, length(zri_values))
for(i in 1:5){
  mod3<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(owners, zri_city>zri_values[i] & zri_city<zri_values[i+1]&affordable=="Half of the units"), cluster=T, respondent.id = "CaseID")
  est3[i]<-summary(mod3)$amce[5,3]
  se3[i]<-summary(mod3)$amce[5,4]
}
mod3ests<-as.data.frame(cbind(zri_values,est3,se3))
mod3ests$uCI<-est3+se3*1.96
mod3ests$lCI<-est3-se3*1.96

est4<-rep(NA, length(zri_values))
se4<-rep(NA, length(zri_values))
for(i in 1:5){
  mod4<-amce(select ~ distance+ community + height + site + tenant + units,
             data=subset(owners, zri_city>zri_values[i] & zri_city<zri_values[i+1]&affordable=="All of the units"), cluster=T, respondent.id = "CaseID")
  est4[i]<-summary(mod4)$amce[5,3]
  se4[i]<-summary(mod4)$amce[5,4]
}
mod4ests<-as.data.frame(cbind(zri_values,est4,se4))
mod4ests$uCI<-est4+se4*1.96
mod4ests$lCI<-est4-se4*1.96

#combine data
mod1<-mod1ests[-6,]
mod1$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod1$modelName<-"None of Units"
names(mod1)<-c("zri","est","se","uci","lci","Quintile","modelName")

mod2<-mod2ests[-6,]
mod2$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod2$modelName<-"Quarter of Units"
names(mod2)<-c("zri","est","se","uci","lci","Quintile","modelName")

mod3<-mod3ests[-6,]
mod3$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod3$modelName<-"Half of Units"
names(mod3)<-c("zri","est","se","uci","lci","Quintile","modelName")

mod4<-mod4ests[-6,]
mod4$quintle<-c("Least Expensive","2nd","3rd","4th","Most Expensive")
mod4$modelName<-"All of Units"
names(mod4)<-c("zri","est","se","uci","lci","Quintile","modelName")

modFrame<-data.frame(rbind(mod1,mod2,mod3,mod4))
modFrame$Quintile <- factor(modFrame$Quintile, levels = c("Least Expensive","2nd","3rd","4th","Most Expensive"))
interval1<-qnorm((1-.9)/2)
interval2<-qnorm((1-.95)/2)
modFrame
modFrame$modelName<-factor(modFrame$modelName, levels=c("None of Units","Quarter of Units","Half of Units","All of Units"))
renters_type_nimby<-ggplot(modFrame, aes(colour=modelName, shape=modelName))+ scale_y_continuous(limits = c(-.3, .3))#+ scale_colour_discrete(name="Affordability") +scale_shape_discrete(name="Affordability")
renters_type_nimby<-renters_type_nimby+theme_bw()+theme(legend.title = element_blank())+scale_colour_grey(end=.5)+geom_hline(yintercept=0, colour=gray(1/2), lty=2)
renters_type_nimby<-renters_type_nimby+geom_linerange(aes( x=Quintile, ymin=est-se*interval1, 
                                                           ymax=est+se*interval1), lwd=1, position=position_dodge(width=1/2))
renters_type_nimby<-renters_type_nimby+geom_pointrange(aes(x=Quintile, y=est, ymin=est-se*interval2,
                                                           ymax=est+se*interval2), lwd=1/2,
                                                       position=position_dodge(width=1/2),  fill="WHITE")
renters_type_nimby<-renters_type_nimby+coord_flip()+ labs(y="Change in Probability Building Preferred", x="Average Rent by City (Quintiles)")
renters_type_nimby<-renters_type_nimby+theme(plot.margin=unit(c(0,0,0,0),"mm"))+ggtitle(("Homeowners, Proximity by Affordability and Average Rent by City"))+guides(colour=guide_legend(reverse=T), shape=guide_legend(reverse=T))


```

```{r Figure C.6 print, echo = FALSE}

print(renters_type_nimby)

```

### Figure C.7. Renter Spatial Sensitivity toward Affordable Housing, by Price Anxiety. Note Lack of Divergence between “Price Anxious” and “Price Neutral” Compared to Preferences toward Market-Rate Housing (Figure 7)

```{r Figure C.7 print, echo = FALSE}

print(renters_anxious_nimby)

```

### Figure C.8. Renter Support for a 10% Increase in Their City/Town’s Housing Supply, Grouped into Quintiles by ZIP Code Average Rent

```{r Figure C.8, include = FALSE, cache = TRUE}

# Figure C.8. Renters Suppport for Supply Cityiwde, Average ZIP Rent ####

quantile(socpoc$zri, probs=seq(0,1,.2), na.rm=T)
zri_city_values<-c(0,1204,1526,1958,2488,13000)
est1<-rep(NA, length(zri_city_values))
se1<-rep(NA, length(zri_city_values))

for(i in 1:5){
  section<-subset(renters, zri>zri_city_values[i] & zri<=zri_city_values[i+1])
  est1[i]<-mean(section$supply_dummy,na.rm=T)
  se1[i]<-sqrt((est1[i]*(1-est1[i]))/nrow(section))
}

mod1ests<-as.data.frame(cbind(zri_city_values,est1,se1))
mod1ests$uCI<-est1+se1*1.96
mod1ests$lCI<-est1-se1*1.96

mod1estimates<-mod1ests[1:5,]
colnames(mod1estimates)<-c("Rent","Estimate", "StdErr", "UpperCI", "LowerCI")
mod1estimates$Quintile<-c(1,2,3,4,5)
mod1estimates
mod1estimates$Cost<-factor(c("Least Expensive","2nd","3rd","4th","Most Expensive"))
levels(mod1estimates$Cost)
pd <- position_dodge(0.1)
mod1estimates$Cost <- factor(mod1estimates$Cost, levels = c("Least Expensive","2nd","3rd","4th","Most Expensive"))
mod1estimates
renter_zip_supply<-ggplot(mod1estimates, aes(x=Cost, y=Estimate))+scale_y_continuous(limits = c(0, 1))+coord_flip()+
  geom_errorbar(aes(ymin=LowerCI, ymax=UpperCI), width=.1, position=pd) +
  geom_point(position=pd)+  labs(x = "Average ZIP Rent (Quintiles)", y="Support for Supply (%)")+ggtitle("Renters Support for Supply Citywide, by Average ZIP Rent") + theme(aspect.ratio = .5)+
  theme_bw()+scale_fill_grey()

```
```{r Figure C.8 print, echo = FALSE}
print(renter_zip_supply)
```

### Figure C.9.  Homeowner Support for a 10% Increase in City/Town’s Housing Supply, by Citywide Average Rent

```{r Figure C.9 code, include = FALSE, cache = TRUE}
# Figure C.9. Homeowners Support for Supply Citywide, Average City Rent ####
quantile(socpoc$zri_city, probs=seq(0,1,.2), na.rm=T)
zri_city_values<-c(0,1217,1480,1936,2427,7344)

est2<-rep(NA, length(zri_city_values))
se2<-rep(NA, length(zri_city_values))

for(i in 1:5){
  section<-subset(owners, zri_city>zri_city_values[i] & zri_city<=zri_city_values[i+1])
  est2[i]<-mean(section$supply_dummy,na.rm=T)
  se2[i]<-sqrt((est2[i]*(1-est2[i]))/nrow(section))
}

mod2ests<-as.data.frame(cbind(zri_city_values,est2,se2))
mod2ests$uCI<-est2+se2*1.96
mod2ests$lCI<-est2-se2*1.96

mod2estimates<-mod2ests[1:5,]
colnames(mod2estimates)<-c("Rent","Estimate", "StdErr", "UpperCI", "LowerCI")
mod2estimates$Quintile<-c(1,2,3,4,5)
mod2estimates
mod2estimates$Cost<-factor(c("Least Expensive","2nd","3rd","4th","Most Expensive"))
levels(mod2estimates$Cost)
pd <- position_dodge(0.1)
mod2estimates$Cost <- factor(mod2estimates$Cost, levels = c("Least Expensive","2nd","3rd","4th","Most Expensive"))
owners_city_supply<-ggplot(mod2estimates, aes(x=Cost, y=Estimate))+scale_y_continuous(limits = c(0, 1))+coord_flip()+
  geom_errorbar(aes(ymin=LowerCI, ymax=UpperCI), width=.1, position=pd) +
  geom_point(position=pd)+ggtitle("Homeowners Support for Supply Citywide, by Average Rent")+
  labs(x = "Average City Rent (Quintiles)", y="Support for Supply (%)")+ theme(aspect.ratio=.5)+
  theme_bw()+scale_fill_grey()

```

```{r Print Figure C.9, echo = FALSE}

print(owners_city_supply)
```











